Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-08-23 doc/GMP2015/revision_3/s04_recombination.tex
Lots of work on Revision 3, getting close.

\begin{theorem}\label{theorem:convexcayley}
    \cite{sitharam2010convex} $H$ has a convexifiable Cayley configuration space  with parameters $F$ if and only if for each $f\in F$  all the minimal 2-sum components of $H\cup F$ that contain both endpoints of $f$ are partial 2-trees. The Cayley configuration space $\Phi_F(H,\delta)$ of a bar-joint system or linkage $(H,\delta)$ is a convex polytope. When $H\cup F$ is a 2-tree, the bounding hyperplanes of this polytope are triangle inequalities relating the lengths of edges of the triangles in $H\cup F$.
\end{theorem}

@@

\begin{theorem}\label{theorem:omdk}
    Given an indecomposable graph $G$, let $G'$ be a spanning partial 2-tree subgraph in $G$ with $k$ fewer edges than $G$. Then $(G,2)$ belongs in the set OMD$_k$.
\end{theorem}

@@

\begin{theorem*}[Efficient search]
\label{theorem:criterionc}
    % [Efficient search]
    For an indecomposable, $k$-approximately convexifiable graph $G = (V,E)$, let $G' = (V,E' =E\setminus D)$ be a spanning partial 2-tree subgraph where $|D| \le  k$. Let  $F$ be a set of non-edges of $G$ such that $H = (V, E'\cup F)$ is a 2-tree. Each solution $p$ (or connected component of a solution space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be found in time $O(\log(W))$ where $W$ is the number of cells of desired accuracy (discrete volume) of the convex polytope $\Phi_F(G',\delta_E')$. The (discrete) volume $W$ is exponential in $|F|$ and polynomial in the (discrete range) of the parameters in $F$.
\end{theorem*}

@@

\ClearMyMinHeight
\SetMyMinHeight{.2}{../../img/epsfromtikz/omd_k33_example_new-0}
\SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example_new-1}
\SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example_new-2}
\SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example-1}
\SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example-2}

\begin{figure*}\centering
    \begin{subfigure}{.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/epsfromtikz/omd_k33_example_new-0}
        \caption{}\label{fig:omd_k33_example:a}
    \end{subfigure}\hfill
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/epsfromtikz/omd_k33_example_new-1}
        \caption{}\label{fig:omd_k33_example:b}
    \end{subfigure}
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/epsfromtikz/omd_k33_example_new-2}
        \caption{}\label{fig:omd_k33_example:c}
    \end{subfigure}\hfill
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/epsfromtikz/omd_k33_example-1}
        \caption{}\label{fig:omd_k33_example:d}
    \end{subfigure}
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/epsfromtikz/omd_k33_example-2}
        \caption{}\label{fig:omd_k33_example:e}
    \end{subfigure}

@@

% \noindent
% \note A major advantage of the convex Cayley method is that it is completely unaffected when $\delta$ are intervals rather than exact values~~\cite{sitharam2010convex}.

\sidenote{A major advantage of the convex Cayley method is that it is completely unaffected when $\delta$ are intervals of values rather than exact values~~\cite{sitharam2010convex}.}
%cite my paper with Heping!!!

>>>>

\begin{theorem}
\label{theorem:convexcayley}
    \cite{sitharam2010convex} $H$ has a convexifiable Cayley configuration space with parameters $F$ if and only if for each $f\in F$ all the minimal 2-sum components of $H\cup F$ that contain both endpoints of $f$ are partial 2-trees. The Cayley configuration space $\Phi_F(H,\delta)$ of a bar-joint system or linkage $(H,\delta)$ is a convex polytope. When $H\cup F$ is a 2-tree, the bounding hyperplanes of this polytope are triangle inequalities relating the lengths of edges of the triangles in $H\cup F$.
\end{theorem}

@@

\begin{theorem}
\label{theorem:omdk}
    Given an indecomposable graph $G$, let $G'$ be a spanning partial 2-tree subgraph in $G$ with $k$ fewer edges than $G$. Then $(G,2)$ belongs in the set OMD$_k$.
\end{theorem}

@@

\begin{theorem*}
[Efficient search]
\label{theorem:criterionc}
    % [Efficient search]
    For an indecomposable, $k$-approximately convexifiable graph $G = (V,E)$, let $G' = (V,E' =E\setminus D)$ be a spanning partial 2-tree subgraph where $|D| \le  k$. Let  $F$ be a set of non-edges of $G$ such that $H = (V, E'\cup F)$ is a 2-tree. Each solution $p$ (or connected component of a solution space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be found in time $O(\log(W))$ where $W$ is the number of cells of desired accuracy (discrete volume) of the convex polytope $\Phi_F(G',\delta_E')$. The (discrete) volume $W$ is exponential in $|F|$ and polynomial in the (discrete range) of the parameters in $F$.
\end{theorem*}

@@

% \ClearMyMinHeight
% \SetMyMinHeight{.2}{../../img/epsfromtikz/omd_k33_example_new-0}
% \SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example_new-1}
% \SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example_new-2}
% \SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example-1}
% \SetMyMinHeight{.15}{../../img/epsfromtikz/omd_k33_example-2}
\ClearMyMinHeight
\SetMyMinHeight{.08}{../../img/svg/k33_omd_a}
\SetMyMinHeight{.08}{../../img/svg/k33_omd_b}
\SetMyMinHeight{.08}{../../img/svg/k33_omd_c}
\SetMyMinHeight{.08}{../../img/svg/k33_omd_d}
\SetMyMinHeight{.08}{../../img/svg/k33_omd_e}

\begin{figure*}\centering
    \hspace{1cm}
    \begin{subfigure}{.08\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/svg/k33_omd_a}
        \caption{}\label{fig:omd_k33_example:a}
    \end{subfigure}\hfill
    \begin{subfigure}{.08\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/svg/k33_omd_b}
        \caption{}\label{fig:omd_k33_example:b}
    \end{subfigure}\hspace{1cm}
    \begin{subfigure}{.08\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/svg/k33_omd_c}
        \caption{}\label{fig:omd_k33_example:c}
    \end{subfigure}\hfill
    \begin{subfigure}{.08\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/svg/k33_omd_d}
        \caption{}\label{fig:omd_k33_example:d}
    \end{subfigure}\hspace{1cm}
    \begin{subfigure}{.08\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/svg/k33_omd_e}
        \caption{}\label{fig:omd_k33_example:e}
    \end{subfigure}
    \hspace{1cm}

@@

Note that a major advantage of the convex Cayley method is that it is completely unaffected when $\delta$ are intervals of values rather than exact values~~\cite{sitharam2010convex}.

### 2015-08-23 doc/GMP2015/revision_3/s06_problempinning.tex
Lots of work on Revision 3, getting close.

\begin{definition}
    A \dfn{body-hyperpin qusecs} is a constraint system where the objects are rigid bodies and the constraints are incidences of object subsets at a common point, i.e.\ a pinning of bodies.
\end{definition}

\begin{remark*}\label{rem:bodypin_is_barjoint}
    A body-hyperpin qusecs is a special case of bar-joint qusecs of the previous sections of the paper. As such, the DR-planning for isostatic systems discussed in Section \ref{sec:DRP} is unchanged and the results of Section \ref{sec:recomb} still go through with minor modifications.
\end{remark*}

@@

\begin{definition}\label{def:body-pin}
    A body-pin graph is a body-hyperpin graph with the following conditions:
    (1) each pin is shared by at most two bodies; and
    (2) no two bodies share more than one pin

@@

\begin{definition}
    A \dfn{triangle-hyperpin graph} is a body-hyperpin graph where each body is a triangle, i.e.\ it shares  pins with at most 3 other bodies. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hypergraphs, {\em 1 and 2-dof} can be characterized by $(2,4)$ and $(2,5)$-tightness respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse}.
\end{definition}

@@

\begin{definition}
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are the bodies.
\end{definition}

@@

As in Section \ref{sec:DRP},  a strong Church-Rosser property holds, making all canonical DR-plans optimal:
%
\begin{observation*}\label{rem:1dofcanon}
    When the input is independent, all $(3,4)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar-joint graphs discussed in Section \ref{sec:DRP}.
\end{observation*}

>>>>

\begin{definition}
[Body-hyperpin qusecs]
    A \dfn{body-hyperpin qusecs} is a constraint system where the objects are rigid bodies and the constraints are incidences of object subsets at a common point, i.e.\ a pinning of bodies.
\end{definition}

\begin{remark*}
\label{rem:bodypin_is_barjoint}
    A body-hyperpin qusecs is a special case of bar-joint qusecs of the previous sections of the paper. As such, the DR-planning for isostatic systems discussed in Section \ref{sec:DRP} is unchanged and the results of Section \ref{sec:recomb} still go through with minor modifications.
\end{remark*}

@@

\begin{definition}
[Body-pin graph]
\label{def:body-pin}
    A \dfn{body-pin graph} is a body-hyperpin graph with the following conditions:
    (1) each pin is shared by at most two bodies; and
    (2) no two bodies share more than one pin

@@

\begin{definition}
[Triangle-hyperpin graph]
    A \dfn{triangle-hyperpin graph} is a body-hyperpin graph where each body is a triangle, i.e.\ it shares  pins with at most 3 other bodies. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hypergraphs, {\em 1 and 2-dof} can be characterized by $(2,4)$ and $(2,5)$-tightness respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse}.
\end{definition}

@@

\begin{definition}
[$(k,l)$-tight DR-plan]
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are the bodies.
\end{definition}

@@

As in Section \ref{sec:DRP},  a strong Church-Rosser property holds, making all canonical DR-plans optimal:
%
\begin{observation*}
\label{rem:1dofcanon}
    When the input is independent, all $(3,4)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar-joint graphs discussed in Section \ref{sec:DRP}.
\end{observation*}

### 2015-08-23 doc/GMP2015/revision_3/s07_pinnedline.tex
Lots of work on Revision 3, getting close.

\begin{definition}
    A \dfn{pinned line-incidence system} $(G,\delta)$ is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \dfn{pins} with fixed positions in $\mathbb{R}^2$, such that each edge is constrained to lie on a line passing through the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
\end{definition}

@@

\begin{definition}
    The \dfn{DR-plan} of a  pinned line-incidence graph $G$ is one in which (1) each child node of a non-leaf node $C$ is either a \dfn{connected} rigid vertex-induced subgraph of $C$, or an edge not contained in any  proper rigid subgraph of $C$, and (2) a leaf node is a single edge.
    % Definition~\ref{def:drp} with  modified rules number 2 and 4:
    %    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
    %    \begin{enumerate}
    %        %\item The root of the tree `contains' $G$.
    %        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any wellconstrained proper subgraph of $C$, or a {\em connected} wellconstrained vertex-maximal proper subgraph of  $C$.
    %        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
    %        \item[4] A node containing a single edge is a leaf.
    %    \end{enumerate}

@@

\begin{observation}\label{lem:pinned_union_intersection}
    Let $F_i$ and $F_j$ to be subgraphs of the same isostatic graph $F$, where each of them can be either a single edge or a connected isostatic subgraph. There are only two possible cases:
    (1) at least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is underconstrained, if and only if $F_i \cap F_j$ is trivial; and (2) both $F_i$ and $F_j$ are isostatic, if and only if $F_i \cup F_j$ is isostatic, if and only if $F_i \cap F_j$ is isostatic.
    %The following table summarizes all bijections:
    %\setlength{\tabcolsep}{3pt}
    %{\small
    %\begin{center}
    %\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
    %\hline
    %\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
    % \centering--- &  \sout{overconstrained}          &  \centering --- \tabularnewline \hline
    %at least one of $F_i,F_j$ is an edge & underconstrained       &  \centering a vertex (underconstrained)  \tabularnewline \hline
    %both $F_i$ and $F_j$ are wellconstrained & wellconstrained        &  \centering wellconstrained  \tabularnewline \hline
    % \centering --- & ---                     &  \centering \sout{underconstrained} \tabularnewline \hline
    %\end{tabular}
    %\end{center}
    %}
    %\setlength{\tabcolsep}{6pt}
\end{observation}

>>>>

\begin{definition}
[Pinned line-incidence system]
    A \dfn{pinned line-incidence system} $(G,\delta)$ is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \dfn{pins} with fixed positions in $\mathbb{R}^2$, such that each edge is constrained to lie on a line passing through the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
\end{definition}

@@

\begin{definition}
[DR-plans of pinned line-incidence systems]
    The \dfn{DR-plan} of a pinned line-incidence graph $G$ is one in which (1) each child node of a non-leaf node $C$ is either a \dfn{connected} rigid vertex-induced subgraph of $C$, or an edge not contained in any  proper rigid subgraph of $C$, and (2) a leaf node is a single edge.
    % Definition~\ref{def:drp} with  modified rules number 2 and 4:
    %    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
    %    \begin{enumerate}
    %        %\item The root of the tree `contains' $G$.
    %        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any wellconstrained proper subgraph of $C$, or a {\em connected} wellconstrained vertex-maximal proper subgraph of  $C$.
    %        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
    %        \item[4] A node containing a single edge is a leaf.
    %    \end{enumerate}

@@

\begin{observation}
\label{lem:pinned_union_intersection}
    Let $F_i$ and $F_j$ to be subgraphs of the same isostatic graph $F$, where each of them can be either a single edge or a connected isostatic subgraph. There are only two possible cases:
    (1) at least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is underconstrained, if and only if $F_i \cap F_j$ is trivial; and (2) both $F_i$ and $F_j$ are isostatic, if and only if $F_i \cup F_j$ is isostatic, if and only if $F_i \cap F_j$ is isostatic.
    %The following table summarizes all bijections:
    %\setlength{\tabcolsep}{3pt}
    %{\small
    %\begin{center}
    %\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
    %\hline
    %\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
    % \centering--- &  \sout{overconstrained}          &  \centering --- \tabularnewline \hline
    %at least one of $F_i,F_j$ is an edge & underconstrained       &  \centering a vertex (underconstrained)  \tabularnewline \hline
    %both $F_i$ and $F_j$ are wellconstrained & wellconstrained        &  \centering wellconstrained  \tabularnewline \hline
    % \centering --- & ---                     &  \centering \sout{underconstrained} \tabularnewline \hline
    %\end{tabular}
    %\end{center}
    %}
    %\setlength{\tabcolsep}{6pt}
\end{observation}
